Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-24 icse/paper.tex
Updating results

\begin{table}[H]
\centering
\begin{tabular}{@{}llll@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{Total}} \\ \midrule
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Class\end{tabular}} & Same Class & 22,893 & \multirow{2}{*}{31,848} \\ \cmidrule(lr){2-3}
 & Same Method & 8,955 &  \\ \midrule
\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Hierarchy\end{tabular}} & Sibling & 15,588 & \multirow{5}{*}{20,342} \\ \cmidrule(lr){2-3}
 & Superclass & 2,616 &  \\ \cmidrule(lr){2-3}
 & First Cousin & 1,219 &  \\ \cmidrule(lr){2-3}
 & Common Hierarchy & 720 &  \\ \cmidrule(lr){2-3}
 & Ancestor & 199 &  \\ \midrule
\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & \multirow{4}{*}{20,314} \\ \cmidrule(lr){2-3}
 & External Superclass & 4,525 &  \\ \cmidrule(lr){2-3}
 & External Ancestor & 3,347 &  \\ \cmidrule(lr){2-3}
 & No Indirect Superclass & 1,765 &  \\ \midrule
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Interface\end{tabular}} & Same Direct Interface & 7,522 & \multirow{2}{*}{13,074} \\ \cmidrule(lr){2-3}
 & Same Indirect Interface & 5,552 &  \\ \bottomrule
\end{tabular}
\caption{Number of clone classes per clone relation}
\label{tab:relation}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{@{}llll@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Location}} & \textit{\textbf{Clone instances}} & \textit{\textbf{Total}} \\ \midrule
\multirow{2}{*}{Partial} & Partial Method & 219,540 & \multirow{2}{*}{229,521} \\ \cmidrule(lr){2-3}
 & Partial Constructor & 9,981 &  \\ \midrule
\multirow{5}{*}{Full} & Full Method & 12,990 & \multirow{5}{*}{13,173} \\ \cmidrule(lr){2-3}
 & Full Interface & 64 &  \\ \cmidrule(lr){2-3}
 & Full Constructor & 58 &  \\ \cmidrule(lr){2-3}
 & Full Class & 37 &  \\ \cmidrule(lr){2-3}
 & Full Enum & 24 &  \\ \midrule
\multirow{3}{*}{Other} & Several Methods & 22,749 & \multirow{3}{*}{53,773} \\ \cmidrule(lr){2-3}
 & Only Fields & 17,700 &  \\ \cmidrule(lr){2-3}
 & Other & 13,324 &  \\ \bottomrule
\end{tabular}
\caption{Number of clone instances for clone location categories}
\label{tab:location}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{All}} & \textit{\textbf{Method Body}} \\ \midrule
Can Be Extracted & 24,157 & 26,109 \\
Is Not A Partial Method & 21,625 & 0 \\
Top-level AST-Node is not a Statement & 19,887 & 4,607 \\
Spans Part of a Block & 13,181 & 13,700 \\
Multiple Return Values & 5,622 & 6,131 \\
Complex Control Flow & 1,106 & 1,216 \\ \bottomrule
\end{tabular}
\caption{Number of clones that can be extracted using the ``Extract Method'' refactoring technique}
\label{tab:refactorability}
\end{table}

>>>>

\begin{table}[H]
\centering
\begin{tabular}{@{}llrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{Total}} \\ \midrule
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Class\end{tabular}} & Same Class & 22,893 & \multirow{2}{*}{31,848} \\ \cmidrule(lr){2-3}
 & Same Method & 8,955 &  \\ \midrule
\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Hierarchy\end{tabular}} & Sibling & 15,588 & \multirow{5}{*}{20,342} \\ \cmidrule(lr){2-3}
 & Superclass & 2,616 &  \\ \cmidrule(lr){2-3}
 & First Cousin & 1,219 &  \\ \cmidrule(lr){2-3}
 & Common Hierarchy & 720 &  \\ \cmidrule(lr){2-3}
 & Ancestor & 199 &  \\ \midrule
\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & \multirow{4}{*}{20,314} \\ \cmidrule(lr){2-3}
 & External Superclass & 4,525 &  \\ \cmidrule(lr){2-3}
 & External Ancestor & 3,347 &  \\ \cmidrule(lr){2-3}
 & No Indirect Superclass & 1,765 &  \\ \midrule
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Interface\end{tabular}} & Same Direct Interface & 7,522 & \multirow{2}{*}{13,074} \\ \cmidrule(lr){2-3}
 & Same Indirect Interface & 5,552 &  \\ \bottomrule
\end{tabular}
\caption{Number of clone classes per clone relation}
\label{tab:relation}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{@{}llrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Location}} & \textit{\textbf{Clone instances}} & \textit{\textbf{Total}} \\ \midrule
\multirow{2}{*}{Partial} & Partial Method & 219,540 & \multirow{2}{*}{229,521} \\ \cmidrule(lr){2-3}
 & Partial Constructor & 9,981 &  \\ \midrule
\multirow{5}{*}{Full} & Full Method & 12,990 & \multirow{5}{*}{13,173} \\ \cmidrule(lr){2-3}
 & Full Interface & 64 &  \\ \cmidrule(lr){2-3}
 & Full Constructor & 58 &  \\ \cmidrule(lr){2-3}
 & Full Class & 37 &  \\ \cmidrule(lr){2-3}
 & Full Enum & 24 &  \\ \midrule
\multirow{3}{*}{Other} & Several Methods & 22,749 & \multirow{3}{*}{53,773} \\ \cmidrule(lr){2-3}
 & Only Fields & 17,700 &  \\ \cmidrule(lr){2-3}
 & Other & 13,324 &  \\ \bottomrule
\end{tabular}
\caption{Number of clone instances for clone location categories}
\label{tab:location}
\end{table}

From these results we see that 74\% of clones span part of a method body (77\% if we include constructors). 8\% of clones span several methods. 6\% of clones span only global variables. Only 4\% of clones span a full declaration (method, class, constructor, etc.).

@@

\begin{table}[H]
\centering
\begin{tabular}{@{}lrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{All}} & \textit{\textbf{\%}} \\ \midrule
Can Be Extracted & 24,157 & 28.2\%  \\
Is Not A Partial Method & 21,625 & 25.3\% \\
Top-level AST-Node is not a Statement & 19,887 & 23.2\% \\
Spans Part of a Block & 12,964 & 15.2\%  \\
Multiple Return Values & 5,622 & 6.6\%  \\
Complex Control Flow & 1,106 & 1.3\% \\
Overlap In Clone Class & 147 & 0.2\% \\
Not In Class Or Interface & 70 & 0.1\% \\
\end{tabular}
\caption{Number of clones that can be extracted using the ``Extract Method'' refactoring technique}
\label{tab:refactorability}
\end{table}
